\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-05 public/paper/pyg4ometry.tex
Paper update

\begin{enumerate}
\item Merging Registries 
\item Removing volumes 
\item Editing solid
\item Converting to assembly solids 
\end{enumerate}
%

\section{Conclusions and discussion}
The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in 
particle transport Monte Carlo programmes will save significant amounts of user effort and ultimately 
yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry 
creation tool, whilst heavily internally based on Geant4 and GDML can have utility for users of all RT 
codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. As for applications, examples 
include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble dark 
matter detectors and geometries for event visualisation. Although not implemented in the current version, 
a C++ output writer can be quickly implemented to generate geometry which can be compiled into a Geant4 
application.

\begin{enumerate}
\item Graphical front end viewer
\item C++ output
\item CAD BREP to FLUKA converter (a la McCAD) 
\item Integration of other tools (DAGMC) 
\item Far from perfect conversions
\item Export mesh for other applications (GPU optics)
\item Convergence FLUKA/Geant4 - Moira 
\item Replace G4 polyhedron CSG
\item Not for large scale conversion
\item Export for other RTMC codes (MCNP, etc) 
\end{enumerate}

>>>>

Having geometry wrapped in a suitable API allows a wide range of processes to be performed simply and potentially 
programmatically if it must be performed for large numbers of objects. The processes include; 
\begin{enumerate}
\item merging registries, 
\item removing volumes (de-featuring),
\item editing solid parameters,
\item replacing logical volume materials 
\item converting logical volumes to assembly volumes.
\end{enumerate}
The merging of registries and removing volumes is required to create the example shown in Figure~\ref{fig:model}. 
Each sub-component is stored in a separate registry and these have to combined without any GDML tags clashing. 
The FLUKA to GDML conversion creates logical volumes which are not generally required in Geant4, so for example
the air surrounding the Faraday cup, which is needed to specify a FLUKA geometry is converted to GDML but can be 
safely removed. Examples of other workflow can be found in the \PYGEOMETRY{} online manual
.
\section{Conclusions and discussion}
The authors believe that tools to quickly create, either ab-initio or by conversion geometry usable in 
particle transport Monte Carlo programmes will save significant amounts of user effort and ultimately 
yield more accurate simulations. \PYGEOMETRY{} is a relatively complete implementation of a geometry 
creation tool, whilst heavily internally based on Geant4 and GDML can have utility for users of all RT 
codes. \PYGEOMETRY{} can clearly be extended to other formats or applications. As for applications, examples 
include  the  generation triangular mesh structures for GPU accelerated photon tracking in liquid noble dark 
matter detectors and geometries for event visualisation. Although not implemented in the current version, 
a C++ output writer can be quickly implemented to generate geometry which can be compiled into a Geant4 
application.

\begin{enumerate}
\item Graphical front end viewer
\item C++ output
\item CAD BREP to FLUKA converter (a la McCAD) 
\item Integration of other tools (DAGMC) 
\item Far from perfect conversions
\item Export mesh for other applications (GPU optics)
\item Convergence FLUKA/Geant4 - Moira 
\item Replace G4 polyhedron CSG
\item Not for large scale conversion
\item Export for other RTMC codes (MCNP, etc) 
\item Performance in Geant4/FLUKA
\end{enumerate}
